Supplementary Material

### 2023-05-05 5 Manuscript/manuscript/supplement/Supplementary_Material.qmd
Finish cross validation, work on supplement

@@

@@

@@

Any additional discussion regarding the supplementary material/findings.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

>>>>

Additionally, a cross-validation approach using tree model was implemented. Prior to machine learning analysis, the data were split into training (75%) and testing (25%) groups. A 5-fold cross-validation, 5 times repeated approach was implemented using MDR as the strata. A tuning grid was utilized using 5 levels of tree depth. After fitting the tree model to the training data, the best model was selected using the area under the receiver operating characteristic curve (ROC AUC). This final model was then fit to the testing data.

@@

Contained below are additional results from both the exploratory and full analyses.

@@

### Tree Model Results

Cost-complexity parameters for various tree depths are shown in Figure 6.

![Figure 6. Cost-complexity Parameter Plot](Supplementary_Material_files/autoplot.png)
Results from the finalized tree model can be found in Figure 7.

![Figure 7. Model Check Metrics for Best-performing LMM](Supplementary_Material_files/rpartplot2.png)

@@

The tree model was ultimately not incorporated into the final manuscript. The ability to account for random effects using the GLMMs and LMMs was better suited for the questions being addressed and the data on hand.
